Behavior Driven Development in Haskell

### 2012-05-25 paper.tex
adding excuse.

TBD: behavior would not be a proper word since Haskell's pure
functions are very static.

>>>>

The word ``behavior'' is associated with actions.
Since pure functions of Haskell are static,
this word might be improper for Haskell.
However, to avoid to define a new terminology,
we use ``behavior'' in this paper.
